% LaTeX CV using moderncv package
\documentclass[10pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.885]{geometry}
\usepackage{lmodern}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt}

% Personal data
\name{Nursultan}{Kuandyk}
\extrainfo{n.kuandyk1995@gmail.com · +7 747 454 8448 · github.com/lunarnuts}
\vspace*{-1.0em}
\begin{document}
\makecvtitle
\setlength{\hintscolumnwidth}{2.2cm} % adjust date column
\renewcommand{\subsectionfont}{\normalsize\bfseries} % optional
\setlength{\parskip}{0.2em} % tighter spacing
\setlength{\parindent}{0pt}

% Summary
\section{Professional Summary}
Results-driven \textbf{Senior Go Software Engineer} with 5+ years designing and scaling cloud-native platforms, high-availability microservices and k8s operators, and event-driven systems across fintech and enterprise domains. Proven record of reducing vulnerabilities by 89\% (eliminating all critical), boosting automated test coverage by 36\% across 60k+ LOC, and delivering APIs with 10k+ RPS at 99.9\% uptime. Skilled at cross-team design alignment, mentoring juniors, and leading modernization initiatives with deep expertise in Go, Kubernetes, gRPC, Kafka, and PostgreSQL.

% Core Skills
\section{Core Skills}
\cvitem{Languages}{Go, JavaScript (Node.js, AngularJS), ABAP}
\cvitem{Architecture}{Clean Architecture, Hexagonal, SOLID, DI; Event-driven and distributed systems}
\cvitem{Cloud/DevOps}{Kubernetes, Docker, AWS, GCP, ArgoCD, GitHub Actions, CI/CD, Operator SDK}
\cvitem{Databases}{PostgreSQL, MySQL, MongoDB, Redis; Query optimization, Transactions, Batching}
\cvitem{Messaging/APIs}{gRPC, Kafka, NATS, REST, OpenAPI 3.0}
\cvitem{Observability}{Grafana, OpenTelemetry, Cribl, SignalFx, Splunk, Loki, Prometheus; Incident response, L3 support}

% Experience
\section{Professional Experience}

\cventry{Jan 2025 -- Present}{Senior Go Software Engineer}{EPAM}{Sofia, Bulgaria}{}{
\begin{itemize}
  \item Played a key part in the development of an operator framework for internal use.
  \item Improved observability by simplifying tech stack using OpenTelemetry collector and splunk(+signalfx)
  \item Built \textbf{Kubernetes operators} to standardize deployments and configuration rollouts, reducing manual ops toils.
  \item Led a team of three engineers to modernize a legacy Node/Angular platform, cutting vulnerabilities from \textbf{228 (28 critical)} to \textbf{26 (0 critical)}, significantly improving security posture and compliance.
  \item Increased automated test coverage by \textbf{36\%} across \textbf{60k+ LOC}, strengthening regression detection and release stability.
  \item Designed and implemented a scalable \textbf{multichannel notification service} supporting in-app, email, and SMS fan-out.
  \item \textbf{Facilitated design sessions across teams} to align API contracts and architectural standards, improving system interoperability.
  \item Mentored middle developers, conducted code reviews, and trained colleagues on Go and cloud-native best practices.
\end{itemize}}

\cventry{Jan 2024 -- Jan 2025}{Senior Go Software Engineer}{DigitalBizFactory}{Astana, Kazakhstan}{}{
\begin{itemize}
  \item Architected and delivered \textbf{core banking APIs} and microservices with worker pools and async schedulers, sustaining \textbf{10k RPS at 99.9\% uptime}.
  \item Introduced \textbf{gRPC} and \textbf{Kafka} to decouple services and enable real-time event streaming; leveraged Redis for caching, prefetching, and rate limiting under peak load.
  \item Optimized PostgreSQL queries and indexes, reducing p95 latency on critical endpoints by \textbf{60\%}.
  \item Partnered with product owners and QA teams to \textbf{refine SLAs}, ensuring compliance with banking regulations.
\end{itemize}}

\cventry{Jan 2023 -- Jan 2024}{Middle Go Software Engineer}{Airba Group}{Almaty, Kazakhstan}{}{
\begin{itemize}
  \item Delivered transaction-safe \textbf{financial APIs} handling millions in monthly volume; automated audit reporting reduced manual preparation time by \textbf{40+ hours/month}.
  \item Optimized banking integrations by batching queries and restructuring transactions, cutting average response times by \textbf{45\%}.
  \item Collaborated with cross-functional teams to enhance compliance and security in financial data handling.
\end{itemize}}

\cventry{Oct 2021 -- Jan 2023}{Junior $\rightarrow$ Middle Software Engineer}{EPAM}{Astana, Kazakhstan}{}{
\begin{itemize}
  \item Developed backend APIs and third-party integrations for a large oil \& gas client, supporting enterprise-scale operations.
\end{itemize}}

% Education
\section{Education}
\cventry{2012 -- 2017}{B.Sc. Robotics \& Mechatronics}{Nazarbayev University}{Astana}{}{}

\end{document}